---
title: "Statistical Inference Cource Project Part2"
author: "Zhang Shiwei"
date: "Saturday, November 22, 2014"
output: pdf_document
---

##Initializing
```{r}
library(knitr)
library(ggplot2)
set.seed(123)
lambda <- 0.2
data <- ToothGrowth
```

##Looking at the data
The structure and brief summary of the data is as following:
```{r}
str(data)
summary(data)
```

This is the polt showing how the len distribute with supp:
```{r}
qplot(data=data,x=len,col=supp,main="Tooth Growth with supp")
```

And this is the poly showing how the len distribute with supp:
```{r}
qplot(data=data,x=len,col=factor(dose),main="Tooth Growth with dose")
```

##Comparation Between Different supp
We assume that the true variance between two supp is not equaled.
```{r}
spliteddata <- split(data,data$supp)
t.test(spliteddata$OJ$len,spliteddata$VC$len,paired=F,var.equal=F,conf.level=0.975)
```

##Comparation Between Different dose
We assume that the true variance between tow dose is not equaled.
```{r}
spliteddata <- split(data,data$dose)
t.test(spliteddata$'0.5'$len,spliteddata$'1'$len,paired=F,var.equal=F,conf.level=0.975)
t.test(spliteddata$'1'$len,spliteddata$'2'$len,paired=F,var.equal=F,conf.level=0.975)
t.test(spliteddata$'2'$len,spliteddata$'0.5'$len,paired=F,var.equal=F,conf.level=0.975)
```